---
title: "ApDungCacMoHinhPhanTich"
author: "Nhom7_DuLieuVeTieuDuong"
date: "2023-12-13"
output: html_document
---

```{r}
install.packages("readr")

```
```{r}
library(readr)
```

STEP-1 : Importing Diabetes Data from Google Drive
```{r}

# Đọc file CSV trực tiếp từ đường link
diabetes <- read_csv("https://drive.google.com/uc?id=15mjrv0LV2T6GWNdAuW-QhXVdtMkQALlh")
# Hiển thị dữ liệu
diabetes

```
STEP-2 : Exploratory Data Analysis on Diabetes Data

Head : head()

Head is a function which returns the first 6 observations of the dataset.
```{r}
head(diabetes)
```
Summary : summary()

Here we are computing the minimum,1st quartile, median, mean,3rd quartile and the maximum for all numeric variables of a dataset at once using summary() function.

```{r}
summary(diabetes)
```
Structure : str()

The structure() function displays the internal structure of a data object.
```{r}
str(diabetes)
```
Column Names : colnames()
The colname() function displays the column names available in the dataset.

```{r}
colnames(diabetes)
```


